A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-02-19 doc/large_strain.tex
minor addition to the roofline interpretation of algorithms

When comparing the data for ``tensor4'' caching strategy (Algorithm \ref{alg:mf_tensor4}) to that from the ``tensor2'' (Algorithm \ref{alg:mf_tensor2}) caching strategy,
we observe a marginal increase in computational intensity and almost unchanged performance.
This coincides with our expectation that the latter algorithm requires transferring fewer bytes to perform operations on a single quadrature point.
On the other hand, the ``scalar'' caching strategy (Algorithm \ref{alg:mf_scalar}) demonstrates a higher computational intensity.
Given that in this case we need to evaluate gradients with respect to both deformed and undeformed configurations, an additional
second-order tensor per quadrature point (inverse of the Jacobian transformation) will be cached as compared to the Algorithm \ref{alg:mf_tensor2}.
As a result both algorithms will have comparable memory requirements (also confirmed by Figures \ref{fig:benchmark_miehe_Emmy_memory2}, \ref{fig:benchmark_miehe_Emmy_memory3}, \ref{fig:benchmark_miehe_IWR_memory2} and \ref{fig:benchmark_miehe_IWR_memory3}),
however the ``scalar'' algorithm performs a large number of repetitive operations that are
independent on the right hand side vector (steps 8--11 in Algorithm \ref{alg:mf_scalar}), which makes it the worst option among the three.

>>>>

When comparing the data for ``tensor4'' caching strategy (Algorithm \ref{alg:mf_tensor4}) to that from the ``tensor2'' (Algorithm \ref{alg:mf_tensor2}) caching strategy,
we observe a marginal increase in computational intensity and almost unchanged performance.
This coincides with our expectation that the latter algorithm requires transferring fewer bytes to perform operations on a single quadrature point
(compare line 9 in Algorithm \ref{alg:mf_tensor4} that loads a symmetric rank-4 tensor to the line 9 in Algorithm \ref{alg:mf_tensor2} that evaluates the
same contraction by loading two scalars $c_1$ and $c_2$).
On the other hand, the ``scalar'' caching strategy (Algorithm \ref{alg:mf_scalar}) demonstrates a higher computational intensity.
This is not surprising as at each quadrature point we need to re-evaluate the Kirchoff stress $\gz \tau$.
Given that in this case we need to evaluate gradients with respect to both deformed and undeformed configurations, an additional
second-order tensor per quadrature point (inverse of the Jacobian transformation) will be cached as compared to the Algorithm \ref{alg:mf_tensor2}.
As a result both algorithms will have comparable memory requirements (also confirmed by Figures \ref{fig:benchmark_miehe_Emmy_memory2}, \ref{fig:benchmark_miehe_Emmy_memory3}, \ref{fig:benchmark_miehe_IWR_memory2} and \ref{fig:benchmark_miehe_IWR_memory3}),
however the ``scalar'' algorithm performs a large number of repetitive operations that are
independent on the right hand side vector (steps 8--11 in Algorithm \ref{alg:mf_scalar}), which makes it the worst option among the three.
